Is high social class always beneficial for survival? Northern Sweden 1801--2013

### 2018-04-17 marginal.Rmd
Small changes

The excess years of remaining life in different social classes compared to workers are shown in Figure \@ref(fig:cumsw2). Concerning the differences in the social pattern, it is less consisten compared to what
we find for the younger age group in the earlier time periods. For women the results are mixed. We do not find the same clear advantage for elite women during the period before 1950, but neither
do we find any large disadvantage for working-class elderly women at that
time. In most periods the social differences were small between working class women and those in the farming and middle catetories. The social differences continued to be small until the last decades of the 20th century. It is only during the four last periods (after the year 1975) that it is
possible to establish the expected social gradient in mortality.

>>>>

The excess years of remaining life in different social classes compared to workers are shown in Figure \@ref(fig:cumsw2). Concerning the differences in the social pattern, it is less consisten compared to what
we find for the younger age group in the earlier time periods. For women the results are mixed. We do not find the same clear advantage for elite women during the period before 1950, but neither
do we find any large disadvantage for working-class elderly women at that
time. In most periods the social differences were small between working class women and those in the farming and middle categories (only differences of a couple of months in median age at death). The social differences continued to be small until the last decades of the 20th century. It is only during the four last periods (after the year 1975) that it is
possible to establish the expected and consistent social gradient in mortality.
